Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-05 acl.2016/acl2016.tex
acl paper

The cube-pruning algorithm contain a further priority queue which is attached to hypotheses sets which can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\STATE initialize $queue_{|C|}$
\FOR{1 to pop-limit}
  \STATE get best $item$ in $queue_{|C|}$
  \STATE create hypo from $item$, coverage $C_{new}$
  \STATE add hypo to $stack_{|C_{new}|}$
  \STATE create next $items$
  \STATE add new $items$ to $queue_{|C|}$
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Cube Pruning with Cardinality Stacks}
\label{algo:Cube Pruning with Unsorted Stack}
\end{figure}
Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|r|r|} \hline
Queue configuration		& Time		& Score \\ \hline
Cardinality			& 192		& -8.59922 \\
Coverage			& 2413		& -8.58635 \\
Coverage \& end position	& 7472		& -8.58263 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
\label{tab:queue-configuration}
\end{table}
From the results in Table~\ref{tab:queue-configuration}, using finer grain queues does results in better model scores but it is significantly slower to decode.

@@

>>>>

The cube-pruning algorithm contain a further priority queue which is attached to hypotheses sets which can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\STATE initialize $queue_{|C|}$
\FOR{1 to pop-limit}
  \STATE get best $item$ in $queue_{|C|}$
  \STATE create hypo from $item$, coverage $C_{new}$
  \STATE add hypo to $stack_{|C_{new}|}$
  \STATE create next $items$
  \STATE add new $items$ to $queue_{|C|}$
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Cube Pruning with Cardinality Stacks}
\label{algo:Cube Pruning with Unsorted Stack}
\end{figure}
Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|r|r|} \hline
Queue configuration		& Time		& Score \\ \hline
Cardinality			& 192		& -8.59922 \\
Coverage			& 2,413		& -8.58635 \\
Coverage \& end position	& 7,472		& -8.58263 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
\label{tab:queue-configuration}
\end{table}
From the results in Table~\ref{tab:queue-configuration}, using finer grain queues does results in better model scores but it is significantly slower to decode.

@@

For any realistic sized phrase-based model to be used in an online situation, memory and loading time constraints requires us to use load-on-demand phrase-table implementations. Moses contains a number of such implementations with different performance characterics, Figure~\ref{fig:moses-phrase-tables-time}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-phrase-table.png}} 
\end{tabular}
\caption{Moses decoding time with different phrase-tables implementations}
\label{fig:moses-phrase-tables-time}
\end{figure} 
We will use the Probing phrase-table (???) exclusively in our work as this appears to have the fastest translation rule lookup, especially with large number of cores.

There are two main areas
